### 2025-09-29 src/articles/article1.qmd
Fix glossary
add scripts and fix extension
fix article linking

# Bylaw Structure

## Bylaws as Pertaining to the International Fraternity

@@

## Amendments

@@

## Suspension

@@

## Interpretation

1. {{< var acronyms.ec >}} will have the power to interpret these Bylaws by an {{< var glossary.absolute-majority >}} vote. 2. Any brother may bring {{< var acronyms.ec >}} Bylaw Interpretation {{< var glossary.grievance >}}s, in writing, to {{< var acronyms.ec >}}.
   a. All {{< var glossary.grievance >}}s brought to {{< var acronyms.ec >}} will, at all times, be confidential.
   a. The results of the {{< var glossary.grievance >}}s will be announced to the chapter at the next chapter meeting.
      i. {{< var acronyms.ec >}} interpretation is subject to overrule by a {{< var glossary.supermajority >}} vote of the active chapter. A. Voting to overrule an {{< var acronyms.ec >}} interpretation of these Bylaws will be done by ballot.

## Glossary

1. All highlighted terms are defined in the Glossary section.
1. The Glossary is a binding section of the bylaws.
1. Amendments to the Glossary will follow the procedure in Article I, Section B.

## Appendices

>>>>

# Bylaw Structure {#sec-art-WEX7K9OS}

## Bylaws as Pertaining to the International Fraternity {#sec-art-5XL0LSV9}

@@

## Amendments {#sec-art-YYQHUMCO}

@@

## Suspension {#sec-art-JKVV6S2J}

@@

## Interpretation {#sec-art-EXPT5HOU}

1. {{< var acronyms.ec >}} will have the power to interpret these Bylaws by an {{< var glossary.absolute-majority >}} vote. 2. Any brother may bring {{< var acronyms.ec >}} Bylaw Interpretation {{< var glossary.grievance >}}s, in writing, to {{< var acronyms.ec >}}.
   a. All {{< var glossary.grievance >}}s brought to {{< var acronyms.ec >}} will, at all times, be confidential.
   a. The results of the {{< var glossary.grievance >}}s will be announced to the chapter at the next chapter meeting.
      i. {{< var acronyms.ec >}} interpretation is subject to overrule by a {{< var glossary.supermajority >}} vote of the active chapter. A. Voting to overrule an {{< var acronyms.ec >}} interpretation of these Bylaws will be done by {{< var glossary.ballot >}}.

## Glossary {#sec-art-40HBGT7N}

1. All highlighted terms are defined in the Glossary section.
1. The Glossary is a binding section of the bylaws.
1. Amendments to the Glossary will follow the procedure in @sec-art-YYQHUMCO.

## Appendices {#sec-art-Q8OV40FK}

### 2025-09-29 src/articles/article10.qmd
fix article linking

# Scholarship

## Scholarship Standards

@@

   a. Any brother with a cumulative Grade Point Average ({{< var acronyms.gpa >}}) of less than 3.0 or an immediately previous semester {{< var acronyms.gpa >}} of less than 3.0 will be placed on {{< var glossary.academic-probation >}} until the end of the semester and will be required to {{< var glossary.attend >}} an Academic Review as described in Article XII, Section K.
      i. The Academic Review must be within the first two weeks of being put on {{< var glossary.academic-probation >}}.

   a. If a brother has a midterm progress {{< var acronyms.gpa >}} of less than 3.0, the Scholarship Chair may request the brother to make a {{< var glossary.grade-improvement-plan >}} in accordance with Article X, Section A, Item 2a.

@@

## New Member Scholarship

1. During the New Member program, the Scholarship Chair will meet with New Members during a regular New Member meeting to explain the chapter Scholarship Program and answer any questions they have.
1. New Members will be held to the academic standards in Article X, Section A.
1. Candidates will be required to sign the grade releases no later than 14 days of grade releases being made available.
1. A candidate is eligible for initiation if they achieved higher than a 3.0 {{< var acronyms.gpa >}} in the previous semester, or if they have a cumulative {{< var acronyms.gpa >}} of greater than 2.5. Upon receiving a Candidate's {{< var acronyms.gpa >}}, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
   a. First semester freshmen are exempt from this rule.
1. Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.
   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an {{< var glossary.absolute-majority >}} vote by the active chapter.

## Privacy

>>>>

# Scholarship {#sec-art-Q7X90PJX}

## Scholarship Standards {#sec-art-1UWTGO5I}

@@

   a. Any brother with a cumulative Grade Point Average ({{< var acronyms.gpa >}}) of less than 3.0 or an immediately previous semester {{< var acronyms.gpa >}} of less than 3.0 will be placed on {{< var glossary.academic-probation >}} until the end of the semester and will be required to {{< var glossary.attend >}} an Academic Review as described in @sec-art-HL5IIDEQ.
      i. The Academic Review must be within the first two weeks of being put on {{< var glossary.academic-probation >}}.

   a. If a brother has a midterm progress {{< var acronyms.gpa >}} of less than 3.0, the Scholarship Chair may request the brother to make a {{< var glossary.grade-improvement-plan >}} in accordance with @sec-art-1UWTGO5I, Item 2a.

@@

## New Member Scholarship {#sec-art-IVGCFY89}

1. During the New Member program, the Scholarship Chair will meet with New Members during a regular New Member meeting to explain the chapter Scholarship Program and answer any questions they have.
1. New Members will be held to the academic standards in @sec-art-1UWTGO5I.
1. Candidates will be required to sign the grade releases no later than 14 days of grade releases being made available.
1. A candidate is eligible for initiation if they achieved higher than a 3.0 {{< var acronyms.gpa >}} in the previous semester, or if they have a cumulative {{< var acronyms.gpa >}} of greater than 2.5. Upon receiving a Candidate's {{< var acronyms.gpa >}}, and finding it does not meet requirements, the Marshal shall announce this at the next regularly scheduled chapter meeting.
   a. First semester freshmen are exempt from this rule.
1. Any Candidate that is ineligible to be initiated will have the option to remain a Candidate.
   a. Should a Candidate remain ineligible in any subsequent semester, they may remain a Candidate only with an {{< var glossary.absolute-majority >}} vote by the active chapter.

## Privacy {#sec-art-7UQDJG9B}

### 2025-09-29 src/articles/article11.qmd
fix article linking

# Expectations of Brothers

## Code of Conduct

@@

## Standards of Brotherhood

1. Financial
   a. Brothers will abide by the financial obligations outlined in Article VI, Section C.

@@

1. Scholarship
   a. Brothers will abide by the scholarship standards described in Article X, Section A. 5. Service
   a. Brothers will complete the service hours assigned to them by the Philanthropy and Service Chair.

@@

   a. Brothers will {{< var glossary.attend >}} chapter meetings as outlined in Article III, Section C.

1. Committees
   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in Article V, Section G.
   a. Brothers will {{< var glossary.attend >}} assigned committee meetings as outlined in Article V, Section G.

## Considerations for Potential New Members

>>>>

# Expectations of Brothers {#sec-art-KJJF9K80}

## Code of Conduct {#sec-art-0MZB8T3Y}

@@

## Standards of Brotherhood {#sec-art-0ERS31Z3}

1. Financial
   a. Brothers will abide by the financial obligations outlined in @sec-art-VDN0D2P4.

@@

1. Scholarship
   a. Brothers will abide by the scholarship standards described in @sec-art-1UWTGO5I.

1. Service
   a. Brothers will complete the service hours assigned to them by the Philanthropy and Service Chair.

@@

   a. Brothers will {{< var glossary.attend >}} chapter meetings as outlined in @sec-art-BUK07FVL.

1. Committees
   a. Brothers will be active members of committees and abide by all relevant bylaws pertaining to the roles and responsibilities of committee members, as detailed in @sec-art-VI2T9PVL.
   a. Brothers will {{< var glossary.attend >}} assigned committee meetings as outlined in @sec-art-VI2T9PVL.

## Considerations for Potential New Members {#sec-art-NH6UEJJ1}

### 2025-09-29 src/articles/article13.qmd
fix article linking

# Chapter Hearings

## Purpose

@@

## Leadership

1. The Vice President of the chapter presides over the hearing as Arbiter. If the Vice President is unable to serve or not present, the Chaplain will preside over the hearing as Arbiter.
1. If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing. If this is not possible, the highest position on Executive Council ({{< var acronyms.ec >}}) will preside over the Chapter Hearing (Article V, Section F, Item 1a) as Arbiter.

## Voting

@@

## Accusation Procedure

1. Chapter Hearings can only be started if the Vice President decides that a Standards Board Hearing should become a Chapter Hearing. As such, the accusation procedure in Article XII, Section F should be used.

## Hearing Preparation

@@

## Hearing Procedure

@@

## Sanctions

>>>>

# Chapter Hearings {#sec-art-BBVW6A2W}

## Purpose {#sec-art-ID5CAL25}

@@

## Leadership {#sec-art-314J6G1Q}

1. The Vice President of the chapter presides over the hearing as Arbiter. If the Vice President is unable to serve or not present, the Chaplain will preside over the hearing as Arbiter.
1. If neither the Vice President nor the Chaplain are able to serve, the Chapter Hearing should be rescheduled to allow at least one of the Vice President or the Chaplain to be available in order to preside over the hearing. If this is not possible, the highest position on Executive Council ({{< var acronyms.ec >}}) will preside over the Chapter Hearing (@sec-art-D3IM05AX, Item 1a) as Arbiter.

## Voting {#sec-art-S4K1I20W}

@@

## Accusation Procedure {#sec-art-C9QQIOS7}

1. Chapter Hearings can only be started if the Vice President decides that a Standards Board Hearing should become a Chapter Hearing. As such, the accusation procedure in @sec-art-1D0EJQ7H should be used.

## Hearing Preparation {#sec-art-1B4EQ2H6}

@@

## Hearing Procedure {#sec-art-CD9I5LLX}

@@

## Sanctions {#sec-art-0CQQ1DK3}

### 2025-09-29 src/articles/article4.qmd
fix article linking

# Voting

## Voting Overview

1. All brothers eligible to vote must vote.
1. Only active brothers who are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. A brother not required to pay local dues is ineligible to vote.
1. Unless specified in Article IV, Section B, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.

## Procedure

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   b. Officer Elections
   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (Article I, Section D)
   d. At a suspension trial
   e. To retain a candidate who was not initiated the previous semester

>>>>

# Voting {#sec-art-D6BOCVLV}

## Voting Overview {#sec-art-GW6C9D29}

1. All brothers eligible to vote must vote.
1. Only active brothers who are not on {{< var glossary.probation >}} or {{< var glossary.financial-probation >}} are eligible to vote.
1. Brothers must be present for all of the discussion on a motion in order to be eligible to vote on that motion.
1. A brother not required to pay local dues is ineligible to vote.
1. Unless specified in @sec-art-N8IIFY4C, or explicitly voted on by {{< var glossary.simple-majority >}}, the method of voting will be by a counted show of hands.

## Procedure {#sec-art-N8IIFY4C}

1. The following votes will be performed by ballot:
   a. New Members for Initiation
   b. Officer Elections
   c. To overturn an Executive Council ({{< var acronyms.ec >}}) Interpretation of the bylaws (@sec-art-EXPT5HOU)
   d. At a suspension trial
   e. To retain a candidate who was not initiated the previous semester

### 2025-09-29 src/articles/article5.qmd
fix article linking

# Officer Selection and Duties

## Terms of Office

@@

## Nominations

@@

## Elections

@@

1. For each elected position the election will proceed as such:
   a. For each candidate:
      i. Candidates will be allowed speeches following these rules:
         1. Other candidates will leave the room.
         1. Candidates will be allowed not less than three minutes to speak.
      i. The chapter will be allowed to ask the candidate questions following these rules:
         1. The chapter will be allowed not less than two minutes to question.
         1. Any time not used by a candidate for his speech will be allowed for questions.
   a. The chapter will discuss the candidates subject to the following rules:
      i. All candidates will leave the room.
      i. The chapter will be allowed not less than five minutes to discuss.
      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.\
   a. Pledges will be allowed to vote in the election in direct exception to the above Article IV, Section A, Item 2.

1. If an elected position should become vacant:
   a. The President will immediately appoint an interim officer, preferably a brother who has held the office before.
   a. Nominations will immediately open for the vacant position, and will close at the next regularly scheduled chapter meeting.
   a. The week following the opening of nominations, elections will proceed as defined above in Article V, Section C.

## Elected Officers and Their Duties

@@

1. Vice President
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix as outlined in Article I, Section F.
   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in Article VII, Section C.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in Article IX, Section C.
   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).\
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in Article V, Section G, Item 3a. o. Must live in the house.

@@

1. Secretary
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in Article III, Section C.
   a. Serves as Secretary of {{< var acronyms.ec >}}.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.

1. Treasurer
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in Article VI, Section B.\
   a. Ensures compliance with the General Rules for chapter finances outlined in Article VI, Section A.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election. A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate. This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter. Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Recruitment Chair
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph l.
   a. Assumes responsibility for directing the recruitment process.
   a. Serves as Chair of the Recruitment Committee.
   a. Will run a recruitment workshop each semester.
   a. Will present a Rush calendar to the chapter by Initiation.
   a. Will be {{< var glossary.responsible >}} for any {{< var glossary.rush-period >}} that they have planned including those after their term.
   a. Confirms and tracks the attendance of each brother at Rush events (Article XI, Section B, Item 2). h. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. First Guard
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph j.
   a. Assists the Marshal in planning and executing initiation and prepares the chapter for it.
   a. Prepares the chapter room for meetings.
   a. Will enforce reasonable dress in the chapter room as stated in Article III, Section D, Item 4.

@@

## Appointed Positions

@@

1. Standards Board At-Large Member
   a. Hears and rules on all cases brought before Standards Board as defined in Article XII.
   a. {{< var glossary.attend >}}s all meetings of Standards Board.
   a. Keeps confidential all matters related to judicial proceedings.
   a. Treats all brothers and New Members fairly, impartially, and consistently.

@@

## Executive Council

@@

1. Purpose, Duties, and Powers
   a. Interprets the bylaws as outlined in Article I, Section D.
   a. Serves as an executive body.
   a. Guides the chapter in emergencies.
   a. Reviews excuses for chapter meetings and other chapter events.
      i. In evaluating excuses, the {{< var acronyms.ec >}} shall adhere to the standards set in the Acceptable Excuses Plan. The Acceptable Excuses Plan shall consist of the following:
         1. Specifically what is an acceptable excuse, with examples.
         1. Specifically what is not an acceptable excuse, with examples.
         1. The number of unexcused absences, missed chapters, and other mandatory events that are allowed per semester before being taken to standards board.
      i. The Acceptable Excuses Plan shall be distributed to the chapter one week before retreat at the beginning of every semester and approved at retreat, with any necessary amendments, as a piece of temporary legislation valid for one semester.
   a. Reviews Requests for {{< var glossary.deferment >}} (Article VI, Section D).
   a. Passes {{< var glossary.executive-edict >}}s as defined in Article II, Section B, Item 4.
   a. Suspends portions of the Bylaws subject to chapter approval as defined in Article I, Section C.
   a. Reviews appeals to {{< var glossary.academic-probation >}} as defined in Article X, Section A.
   a. Meets with respective {{< var acronyms.cab >}} member once a month.
   a. Appoints appointed positions.

@@

## Committees

1. The chapter will have the following groups of committees:
   a. Standard Committees
      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
         1. Alumni Relations Committee and Member Development Committee
         1. Health and Safety Committee and Scholarship Committee
         1. Philanthropy and Service Committee and Social Committee
         1. Public Relations Committee and Recruitment Committee
      i. All Standard committees will do the following:
         1. Meet at least once every two weeks as directed by their chair.
            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1. Assist the chair in the discharge of their duties.
         1. Create a set of goals for the committee at the first meeting of the committee.
         1. Work toward the goals of the committee.
   b. Operational Committees\
      i. Ad hoc committees
         1. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1. Purpose and Duties
            a. To create a budget for the chapter for the next year pursuant to Article VI, Section B. 2. To examine any financial issues of the chapter.
         1. Membership
            a. The Treasurer will serve as chair of the Budget Committee.
            a. The body of the committee will be selected by the Treasurer.
         1. Procedure
            a. The committee will be created and convened during the budgeting process outlined in Article VI, Section B, Item 3.
            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
      i. Committee Chair Committee ({{< var acronyms.ccc >}})
         1. Purpose
            a. To facilitate communication between committee chairs.
            a. To keep the Vice President informed of committee business.
            a. To help the Vice President ensure that committees are performing all necessary duties.
         1. Membership
            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
            a. The chairs of all Standard Committees will be members.
            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
         1. Procedure
            a. The committee will meet at least once every two weeks while school is in session. 2. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1. The Mandatory Bylaw Revision Committee will function in accordance with Article IX, Section C.

>>>>

# Officer Selection and Duties {#sec-art-F8LOE4WJ}

## Terms of Office {#sec-art-3MIFLS7V}

@@

## Nominations {#sec-art-NUXDQ4I0}

@@

## Elections {#sec-art-3AOCUCRJ}

@@

1. For each elected position the election will proceed as such:
   a. For each candidate:
      i. Candidates will be allowed speeches following these rules:
         1. Other candidates will leave the room.
         1. Candidates will be allowed not less than three minutes to speak.
      i. The chapter will be allowed to ask the candidate questions following these rules:
         1. The chapter will be allowed not less than two minutes to question.
         1. Any time not used by a candidate for his speech will be allowed for questions.
   a. The chapter will discuss the candidates subject to the following rules:
      i. All candidates will leave the room.
      i. The chapter will be allowed not less than five minutes to discuss.
      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.\
   a. Pledges will be allowed to vote in the election in direct exception to the above @sec-art-GW6C9D29, Item 2.

1. If an elected position should become vacant:
   a. The President will immediately appoint an interim officer, preferably a brother who has held the office before.
   a. Nominations will immediately open for the vacant position, and will close at the next regularly scheduled chapter meeting.
   a. The week following the opening of nominations, elections will proceed as defined above in @sec-art-3AOCUCRJ.

## Elected Officers and Their Duties {#sec-art-YZW2AQAI}

@@

1. Vice President
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix as outlined in @sec-art-Q8OV40FK.
   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in @sec-art-C89656BJ.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in @sec-art-YOSPIQLS.
   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).\
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in @sec-art-VI2T9PVL, Item 3a. o. Must live in the house.

@@

1. Secretary
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph d.
   a. Records attendance and enforces the standards for attendance in @sec-art-BUK07FVL.
   a. Serves as Secretary of {{< var acronyms.ec >}}.
   a. Collects all legislation, Bylaw amendments, and Officer Reports.
   a. Sets the agenda for chapter meetings according to the {{< var acronyms.ibl >}} Article V, Section 8, paragraph d.
   a. Maintains the mailbox and mail closet.
   a. Will create a contact list for the chapter which includes contact information of brothers advisors, Greek Life, and emergency services.
   a. Handles registration of Pledges, requests for initiation, and the recording of new initiates.

1. Treasurer
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother. The report will include all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.\
   a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election. A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate. This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter. Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Recruitment Chair
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph l.
   a. Assumes responsibility for directing the recruitment process.
   a. Serves as Chair of the Recruitment Committee.
   a. Will run a recruitment workshop each semester.
   a. Will present a Rush calendar to the chapter by Initiation.
   a. Will be {{< var glossary.responsible >}} for any {{< var glossary.rush-period >}} that they have planned including those after their term.
   a. Confirms and tracks the attendance of each brother at Rush events (@sec-art-0ERS31Z3, Item 2). h. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. First Guard
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph j.
   a. Assists the Marshal in planning and executing initiation and prepares the chapter for it.
   a. Prepares the chapter room for meetings.
   a. Will enforce reasonable dress in the chapter room as stated in @sec-art-8XE7XCGC, Item 4.

@@

## Appointed Positions {#sec-art-QQ786XUW}

@@

1. Standards Board At-Large Member
   a. Hears and rules on all cases brought before Standards Board as defined in @sec-art-IHXJUPV0.
   a. {{< var glossary.attend >}}s all meetings of Standards Board.
   a. Keeps confidential all matters related to judicial proceedings.
   a. Treats all brothers and New Members fairly, impartially, and consistently.

@@

## Executive Council {#sec-art-D3IM05AX}

@@

1. Purpose, Duties, and Powers
   a. Interprets the bylaws as outlined in @sec-art-EXPT5HOU.
   a. Serves as an executive body.
   a. Guides the chapter in emergencies.
   a. Reviews excuses for chapter meetings and other chapter events.
      i. In evaluating excuses, the {{< var acronyms.ec >}} shall adhere to the standards set in the Acceptable Excuses Plan. The Acceptable Excuses Plan shall consist of the following:
         1. Specifically what is an acceptable excuse, with examples.
         1. Specifically what is not an acceptable excuse, with examples.
         1. The number of unexcused absences, missed chapters, and other mandatory events that are allowed per semester before being taken to standards board.
      i. The Acceptable Excuses Plan shall be distributed to the chapter one week before retreat at the beginning of every semester and approved at retreat, with any necessary amendments, as a piece of temporary legislation valid for one semester.
   a. Reviews Requests for {{< var glossary.deferment >}} (@sec-art-OUD16M61).
   a. Passes {{< var glossary.executive-edict >}}s as defined in @sec-art-9HMJ9WUB, Item 4.
   a. Suspends portions of the Bylaws subject to chapter approval as defined in @sec-art-JKVV6S2J.
   a. Reviews appeals to {{< var glossary.academic-probation >}} as defined in @sec-art-1UWTGO5I.
   a. Meets with respective {{< var acronyms.cab >}} member once a month.
   a. Appoints appointed positions.

@@

## Committees {#sec-art-VI2T9PVL}

1. The chapter will have the following groups of committees:
   a. Standard Committees
      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
         1. Alumni Relations Committee and Member Development Committee
         1. Health and Safety Committee and Scholarship Committee
         1. Philanthropy and Service Committee and Social Committee
         1. Public Relations Committee and Recruitment Committee
      i. All Standard committees will do the following:
         1. Meet at least once every two weeks as directed by their chair.
            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1. Assist the chair in the discharge of their duties.
         1. Create a set of goals for the committee at the first meeting of the committee.
         1. Work toward the goals of the committee.
   b. Operational Committees\
      i. Ad hoc committees
         1. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1. Purpose and Duties
            a. To create a budget for the chapter for the next year pursuant to @sec-art-GD7C1K2U.
            a. To examine any financial issues of the chapter.
         1. Membership
            a. The Treasurer will serve as chair of the Budget Committee.
            a. The body of the committee will be selected by the Treasurer.
         1. Procedure
            a. The committee will be created and convened during the budgeting process outlined in @sec-art-GD7C1K2U, Item 3.
            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
      i. Committee Chair Committee ({{< var acronyms.ccc >}})
         1. Purpose
            a. To facilitate communication between committee chairs.
            a. To keep the Vice President informed of committee business.
            a. To help the Vice President ensure that committees are performing all necessary duties.
         1. Membership
            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
            a. The chairs of all Standard Committees will be members.
            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
         1. Procedure
            a. The committee will meet at least once every two weeks while school is in session.
            a. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1. The Mandatory Bylaw Revision Committee will function in accordance with @sec-art-YOSPIQLS.
